---
title: "hw03(2)"
author: "Sejal Keshvara"
date: "2/22/2020"
output: 
  github_document: defualt
  html_document: default 
  ---
  
# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.

```{r}
dictionary <- readr::read_csv(here::here("hw03", "green_dictionary.csv"))
green_data <- readr::read_csv(here::here("hw03", "green_data (1).csv"))
```
```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
library(tibble)
library(tidyverse)
library(scales)
```

For your assignment, do the following.

  1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). 
     Is anything unusual?
     
```{r}
summary(green_data)
```

```{r}

summary(green_data)

green_data_missingvalues <- green_data %>% 
  mutate(
    across(.cols = everything(), 
           ~na_if(.x, "-99")
           )
  ) %>% 
    
mutate(
  student = recode(student, "1" = "nonstudent", "2" = "student"))


```
# There is an unusal set of values in the data set. That is why the value -99 was recoded to NA.  


  2. Compute total scores for the four scales. 
  
```{r}

reversed <- dictionary %>% 
  filter(Keying == -1 | Keying == -2) %>%
  pull(Item)
reversed
# Recoding the variables 
green_reversed <- green_data_missingvalues %>%
  mutate(
    across(all_of(reversed),
          ~recode(.x,"5" = 1, "4" = 2, "3" = 3, "2" = 4, "1" = 5) )
  )
  
#Computing the total scores for all four scales. 

green_total_values <- green_reversed %>% 
  rowwise() %>% 
  mutate(
    Green_total = mean(c_across(green1:green5)), trim = 0, na.rm =TRUE, 
    Comp_total = mean(c_across(comp1:comp10)), trim = 0, na.rm = TRUE,
    Intel_total = mean(c_across(intel1:intel10)), trim = 0, na.rm = TRUE,
    Open_total = mean(c_across(open1:open10)), trim = 0, na.rm = TRUE,
  ) %>% 
  
select(id, student, Green_total, Comp_total, Intel_total, Open_total)


```
     Recode variables as needed.
  3. Rescale the variables so that they go from 0-100 instead of the original range.
     Name the recaled variables `*_pomp`.
     
```{r}
green_rescaled <- green_total_values %>%
  mutate(
    Green_pomp = rescale(Green_total, to = c(0,100), from = c(1,5)), 
    Comp_pomp = rescale(Comp_total, to = c(0,100), from = c(1,5)), 
    Intel_pomp = rescale(Intel_total, to = c(0,100), from = c(1,5)),
    Open_pomp = rescale(Open_total, to = c(0,100), from = c(1,5)),
    ) %>% 
select(id, student, Green_pomp, Comp_pomp, Intel_pomp, Open_pomp)
```
  4. Make plots that illustrate the distributions of the 4 POMP-scored variables.
  
```{r}
#Histograms 

#Histogram for Green_pomp
ggplot(green_rescaled, aes(x = Green_pomp)) +
  geom_histogram(binwidth = 2)

#Histogram for Comp_pomp
ggplot(green_rescaled, aes(x = Comp_pomp)) +
  geom_histogram(binwidth = 2)

#Histogram for Intel_pomp
ggplot(green_rescaled, aes(x = Intel_pomp)) +
  geom_histogram(binwidth = 2)

#Histogram for Open_pomp
ggplot(green_rescaled, aes(x = Open_pomp)) +
  geom_histogram(binwidth = 1.5)


```
  5. Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
     
```{r}
green_rescaled %>% 
ggplot() +
  aes(x = Green_pomp, y = Comp_pomp, group = student, color = student, fill = student) +
    geom_jitter()
      geom_smooth(method = lm)
# This plot shows that Openness positively correlates with Green reputation in both students and non students. 

green_rescaled %>% 
  ggplot() +
    aes(x = Green_pomp, y = Intel_pomp, group = student, color = student, fill = student) +
      geom_jitter()
        geom_smooth(method = lm)


        
green_rescaled %>% 
  ggplot() +
    aes(x = Green_pomp, y = Open_pomp, group = student, color = student, fill = student) +
      geom_jitter() +
        geom_smooth(method = lm)

```
  6. Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).
  
```{r}
green_rescaled %>% 
  ggplot(
    aes(x = Green_pomp, color = student), alpha = 1) +
      geom_bar() +
      geom_density() +
      geom_point(aes(y = "trait", color = student), alpha = 1)

```
  7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
```{r}
green_rescaled %>%
  select(id, student, Green_pomp, Comp_pomp, Intel_pomp, Open_pomp) %>% 
    group_by(student) %>% 
      summarise(across(c(Green_pomp, Comp_pomp, Intel_pomp, Open_pomp)),  
          list(
            Mean = ~mean(.x, na.rm = TRUE),
            Sd = ~sd(.x, na.rm = TRUE),
            Median = ~median(.x, na.rm = TRUE),
            Min = ~min(.x, na.rm = TRUE),
            Max = ~max(.x, na.rm = TRUE)
          )
      )
  

```
In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.
