---
title: "hw03(2)"
author: "Sejal Keshvara"
date: "2/22/2020"
output: 
  github_document: defualt
  html_document: default 
  ---
  
# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.

```{r}
dictionary <- readr::read_csv(here::here("hw03", "green_dictionary.csv"))
green_data <- readr::read_csv(here::here("hw03", "green_data (1).csv"))
```
```{r}
library(dplyr)
library(ggplot2)
```

For your assignment, do the following.

  1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). 
     Is anything unusual?
     
```{r}
summary(green_data)
```

```{r}
#green_data <- na_if(green_data, "-99")

green_data_missingvalues <- green_data %>% 
  mutate(
    across(.cols = everything(),
           ~na_if(.x, "-99")
           )
  )

```
# There is an unusal set of values in the data set. That is why the value -99 was recoded. 


  2. Compute total scores for the four scales. 
  
```{r}




```
     Recode variables as needed.
  3. Rescale the variables so that they go from 0-100 instead of the original range.
     Name the recaled variables `*_pomp`.
  4. Make plots that illustrate the distributions of the 4 POMP-scored variables.
  5. Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
  6. Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).
  7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
  
In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.
