---
title: "final_project"
author: "Sejal Keshvara"
date: "05-02-2021"
output: 
  html_document: default
  github_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readr)
library(dplyr)
library(ggplot2)
library(scales)
library(lubridate)

```

```{r}
url <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/us-weather-history/KCLT.csv"

weather_data <- read_csv(url)

print(weather_data)

```


#Since the dataframe is already cleaned out (there are no missing values or 0's) I moved on to grouping the data columns in a certain way. 

```{r}





```

#This dataframe includes the average as well as actual temperatures and precipitation levels in the United States from 2014 to 2015. 

#This plot is to show how the average maximum temperatures compare to the average minimum temperatures. 

```{r}

df <- select(weather_data, date, average_min_temp, average_max_temp)
ggplot(df, aes(as.Date(date), y = value, color = variable)) + 
    geom_point(aes(y = average_max_temp, col = "Average Maximum Temperatures")) + 
    geom_point(aes(y = average_min_temp, col = "Average Minimum Temperatures"))


```

#Here we compare the actual minimum and the actual maximum temperatures in the united states from the years 2014 to 2015. 
```{r}
df <- select(weather_data, date, actual_max_temp, actual_min_temp)
  ggplot(df, aes(as.Date(date), y = value, color = variable)) +
    geom_point(aes(y = actual_max_temp, col = "Actual Maximum Temperatures")) +
    geom_point(aes(y = actual_min_temp, col = "Actual Minimum Temperatures"))


```

#The actual and average minmimum temperatures are compared on the scatter plot. I was interested in finding out how the temperatures from 2014-2105 compare to the average temperatures. 

```{r}
df <- select(weather_data, date, average_min_temp, actual_min_temp)
  ggplot(df, aes(as.Date(date), y = "Temperature", color = "blue")) +
    geom_point(aes(y = average_min_temp, col = "Average Minimum Temperatures")) +
    geom_point(aes(y = actual_min_temp, col = "Actual Minimum Temperatures"))


```
# What I found from the scatter plot was that the temperatures have stayed fairly consistent with the average temperatures although it seems that during the summer months, the actual minimum temperatures 





```{r}
df <- select(weather_data, date, average_max_temp, actual_max_temp)
  ggplot(df, aes(as.Date(date), y = "Temperature", color = "green")) +
    geom_point(aes(y = average_max_temp, col = "Average Maximum Temperatures")) +
    geom_point(aes(y = actual_max_temp, col = "Actual Maximum Temperatures"))


```





#Now I wanted to compare the actual and average precipitation within the years of 2014-2015. 

```{r}
df <- select(weather_data, date, actual_precipitation, average_precipitation)
  ggplot(df, aes(as.Date(date), y =value, color = variable)) +
    geom_point(aes(y = actual_precipitation, col = "Actual Precipitation")) +
    geom_point(aes(y = average_precipitation, col = "Average Precipitation"))


```


#The values are grouped together based on the year they occured in. 

```{r}
df3 <- select(weather_data, date, record_precipitation)
  df3 %>% 
  mutate(date = as.Date(date)) %>% 
  mutate(y = format(date, '%Y')) %>% 
  group_by(y)

```